---
title: "Congressional Record Data"
subtitle: 
author: ""
output:
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)

library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Join Congressional Record speech data with Voteview data

## Starting with Hein-bound records

```{r}
# a function to read speaker data 
get_speakers <- function(file){
  
  message(file)
  
  read_delim(str_c(here("hein-bound/", file) %>% str_remove("/cr") ),
           delim = "|") %>% 
  # drop speech data for now
  select(-speech_id) %>% 
  # extract congress from file name
  mutate(congress = str_remove(file, "_.*") ) %>% 
  distinct()
}

# files 
heinbound <- list.files(here("hein-bound") %>% str_remove("/cr") ) %>% 
  enframe(value = "file")

# subset to speakermap files from recent congresses
speakermaps <- heinbound %>% 
  filter(str_detect(file, "SpeakerMap"),
         str_detect(file, "^1") #FIXME subsetting to >99th congress
         )

# speakers dataframe
speakers <- map_dfr(speakermaps$file,
        get_speakers)

# match to voteview format 
speakers %<>% 
  mutate(last_name = lastname,
         first_name = str_to_sentence(firstname),
         congress = congress %>% str_remove("^0") %>% as.numeric(),
         chamber = chamber %>% 
           str_replace("S$", "Senate") %>% 
           str_replace("H$", "House"),
         district_code = ifelse(chamber == "Senate", 0, district) %>% as.numeric()
         ) 

speakers %<>% 
  rename(state_abbrev = state)

# FIXME focusing on the 107-111th for now 
speakers %<>% 
  filter(congress > 107) 

# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))
# members %>% select(names(members)[names(members) %in% names(speakers)])

# Make mixed case names, like "McConnell" upper (to go the other way, we would need to fix them one by one)
members %<>% 
  mutate(last_name = str_to_upper(last_name),
         party = str_sub(party_name, 1, 1))
```

### Unfortunately, first names not consistent across datasets. 

```{r}
speakers %>% 
  select( -district_code) %>%
  anti_join(members) %>% 
  select(-first_name) %>% 
  left_join(members) %>% 
  select(voteview_first_name = first_name,
         speakermap_firstname = firstname, 
         lastname) %>% 
  distinct() %>% 
  arrange(lastname) %>% kablebox()
```

---


### Some observations in the Hein records are missing district information.

(Hereth Sandlin, Cubin, Rehberg, Young), making them fail to match.

### Because they don't have voting records, non-voting members are not in the Voteview data. 

If we drop first names and districts, we match almost all voting members, but we also over-match.

Mary Bono Mack also fails to match because she is just Mary Bono in Voteview. 

```{r}
# mismatches 
speakers %>% 
  select(-first_name) %>%
  anti_join(members) %>% 
  kablebox()
```

---

Without matching on first names, we get duplicate matches, e.g., André CARSON was appointed to fill the seat of his grandmother, Julia May CARSON:

```{r}
# overmatches in speakers data
speakers %>% 
  count(congress, chamber, last_name, state_abbrev, party, district) %>%
  filter(n>1) %>% 
  kablebox()

# potential overmatches
members %>% 
  count(congress, chamber, last_name, state_abbrev, party, district_code) %>%
  filter(n>1) %>% 
  kablebox()
```

---

Without matching on first names OR districts (because of missing district data), we get even more duplicate/potential duplicate matches.

```{r}
# overmatches in speakers data
speakers %>% 
  count(congress, chamber, last_name, state_abbrev, party) %>%
  filter(n>1) %>% 
  kablebox()

# potential overmatches
members %>% 
  count(congress, chamber, last_name, state_abbrev, party) %>%
  filter(n>1) %>% 
  kablebox()
```

