---
title: "Congressional Record Data"
subtitle: 
author: ""
output:
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Join Congressional Record speech data with Voteview data

## Starting with Hein-bound records

```{r}
# a function to read speaker data 
get_speakers <- function(file){
  
  message(file)
  
  read_delim(str_c(here("hein-bound/", file) %>% str_remove("/cr") ),
             delim = "|") %>% 
  # drop speech data for now
  select(-speech_id) %>% 
  # extract congress from file name
  mutate(congress = str_remove(file, "_.*") ) %>% 
  distinct()
}

# files 
heinbound <- list.files(here("hein-bound") %>% str_remove("/cr") ) %>% 
  enframe(value = "file")

# subset to speakermap files from recent congresses
speakermaps <- heinbound %>% 
  filter(str_detect(file, "SpeakerMap"),
         str_detect(file, "^1") #FIXME subsetting to >99th congress
         )

# speakers dataframe
speakers <- map_dfr(speakermaps$file, get_speakers)

# match to voteview format 
speakers %<>% 
  mutate(last_name = lastname,
         first_name = str_to_sentence(firstname),
         congress = congress %>% str_remove("^0") %>% as.numeric(),
         chamber = chamber %>% 
           str_replace("S$", "Senate") %>% 
           str_replace("H$", "House"),
         district_code = ifelse(chamber == "Senate", 0, district),
         # clean up some 0s that are actually missing data 
         district_code =  ifelse(chamber == "House" & district_code == "0", NA, district_code) %>% 
           as.numeric() 
         ) 

speakers %<>% 
  rename(state_abbrev = state)

# FIXME focusing on the 107-111th for now 
speakers %<>% 
  filter(congress > 106)


# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))
# members %>% select(names(members)[names(members) %in% names(speakers)])

# Make mixed case names, like "McConnell" upper case (to go the other way, we would need to fix them one by one)
members %<>% 
  mutate(last_name = str_to_upper(last_name),
         party = str_sub(party_name, 1, 1))
```

### Unfortunately, first names are not consistent across datasets. 

### Because they don't have voting records, non-voting members are not in the Voteview data.

A few last names also differ, e.g. Mary Bono Mack also fails to match because she is just Mary Bono in Voteview. 

```{r}
speakers %>% 
  select( -district_code) %>%
  anti_join(members) %>% 
  select(-first_name) %>% 
  left_join(members) %>% 
  select(voteview_first_name = first_name,
         speakermap_firstname = firstname, 
         lastname, nonvoting) %>% 
  distinct() %>% 
  arrange(lastname) %>% kablebox()
```

---


### Some observations in the Hein records are missing district information.

(Hereth Sandlin, Cubin, Rehberg, Young)






```{r}
# mismatches 
speakers %>% 
  select(-first_name) %>%
  anti_join(members) %>% 
  kablebox()
```

---

If we drop first names and districts, we match almost all voting members, but we also over-match.

Without matching on first names, we get duplicate matches, e.g., André CARSON was appointed to fill his grandmother's seat, Julia May CARSON:

```{r}
# overmatches in speakers data
speakers %>% 
  count(congress, chamber, last_name, state_abbrev, party, district) %>%
  filter(n>1) %>% 
  kablebox()

# potential overmatches
members %>% 
  count(congress, chamber, last_name, state_abbrev, party, district_code) %>%
  filter(n>1) %>% 
  kablebox()
```

---

Without matching on first names OR districts (because of missing district data), we get even more duplicate/potential duplicate matches.

```{r}
# overmatches in speakers data
speakers %>% 
  count(congress, chamber, last_name, state_abbrev, party) %>%
  filter(n>1) %>% 
  kablebox()

# potential overmatches
members %>% 
  count(congress, chamber, last_name, state_abbrev, party) %>%
  filter(n>1) %>% 
  kablebox()
```

## fastLink

Just for fun, we'll give this a try, even though we have a custom solution. fastLink returns a match for voting members.

```{r}
library(fastLink)

fl.out <- fastLink(speakers, 
                   members, 
                   varnames = c("chamber", "state_abbrev", "party", "congress", "last_name", "first_name", "district_code"), return.df = T, return.all = F)

speakers %>% filter(nonvoting == "voting") %>% nrow()
fl.out$dfA.match %>%  nrow()
fl.out$dfA.match %>% head() %>% kablebox()
fl.out$dfB.match %>% head() %>% kablebox()

fl.speakers <- fl.out$dfA.match %>% 
  mutate(icpsr = fl.out$dfB.match$icpsr,
         bioname = fl.out$dfB.match$bioname,
         party_name = fl.out$dfB.match$party_name,
         district_code_voteview = fl.out$dfB.match$district_code) %>% 
  full_join(speakers)

# failed matches
fl.speakers %>% filter(is.na(icpsr)) %>% kablebox()

# party mismatches 
fl.speakers %>% filter(party != party_name %>% str_sub(1, 1)) %>%
  select(party, party_name, everything()) %>% 
  kablebox()

# district mismatches 
# fl.speakers %>% filter(district_code != district_code_voteview) %>% kablebox()
```

## Custom name matching function

```{r}
# start with fresh data (can eventually delete everything above up to map function if we use this method)

# speakers dataframe
speakers <- map_dfr(speakermaps$file, get_speakers)

# match to voteview format 
speakers %<>% 
  mutate(congress = congress %>% str_remove("^0") %>% as.numeric(),
         chamber = chamber %>% 
           str_replace("S$", "Senate") %>% 
           str_replace("H$", "House"),
         district = ifelse(chamber == "Senate", 0, district),
         # clean up some 0s that are actually missing data 
         district =  ifelse(chamber == "House" & district == "0", NA, district) %>% 
           as.numeric() 
         ) 

speakers %<>% 
  rename(state_abbrev = state)

# FIXME focusing on the 107-111th for now 
speakers %<>% 
  filter(congress > 106)

speakers %<>% 
  # combine information into one field
  mutate(speaker = paste(chamber, firstname, lastname, state_abbrev) %>% 
           str_replace("Senate", "Senator") %>% 
           str_replace("House", "Representative") %>% 
           str_replace("Representative R\\.", "Representative"))

# name matching function 
source(here("code", "nameMethods.R"))

# typos in these data include "WM" instead of "William" and "R. Miller" for "Representative Brad Miller", the rest are known permutations and nicknames 
source(here("code", "MemberNameTypos.R"))

speakers1 <- speakers %>% extractMemberName(col_name = "speaker", members = members)

# FIXME, overmatches party switchers (and maybe others)
crosswalk <- speakers1 %>% 
  select(speaker, speakerid, icpsr, bioname, congress, chamber, nonvoting) %>%
  distinct()  %>% 
  left_join(members %>% 
              select(icpsr, congress, chamber, state_abbrev, party_name, district_code)) %>%
  distinct()
```

### Failed to match with voteview on name, chamber, state

My congressional name search function gets us 100% matches when we don't use party information, but party-switchers get an ICPSR for both parties. When we match on party, we find that some party info in the speakers data are incorrect. 

```{r}
# failed to match in crosswalk
crosswalk %>% filter(is.na(icpsr) & nonvoting == "voting") %>%
  kablebox()
```


### Failed to match when including party

Missing district data in the speakers data is fine; we can fill it in from voteview. 

I have not yet found incorrect districts, but these would cause this to fail (and rightly so, getting the district right is important!).

However, the speakers data has a few incorrect parties. 
-Crenshaw was never an independent 
-alexander was a D in the 108th
-specter switched in 2009 (11th), he was not a D in the 109 or 110
-Lieberman called himself an "independent Democrat" and caucused with the Ds, so he is only a D in voteview

These can be corrected, or we can use those from voteview if we decided to go with their first party or modal party. There are likely more instances in the speakers data where their party is coded inconsistently with either principle.


This result is identical to fastLink.

```{r}
# failed to match in data 
test <- speakers %>% 
  left_join(crosswalk) %>% 
  left_join(members %>% select(icpsr, chamber, congress, state_abbrev, party_name, district_code) %>% distinct()) %>% 
  # require district match where there is district data in speaker data
  filter((district == district_code | is.na(district) ) ) %>% 
  # drop party switchers
  filter(party == str_sub(party_name, 1,1) | is.na(party_name)) %>% 
  distinct()



speakers %>%
  anti_join(test) %>% 
  select(party, everything()) %>%
  kablebox()
```


# Questions 
- should I correct speakers data party by hand or replace it in a principled way with with voteview? (not a big deal either way). I suggest going with voteview, and picking D or R over I when unknown. This depends on how important it is to keep this party in this dataset perfectly consistant with the speakers data, which does not seem important.

# Notes

## TODO

- we are ignoring incorrect parties (and thus ICPSRs) assigned to party-switchers for now. Eventually, we will need to look up the first speech that a switcher made and re-code their party for speeches after that (assuming that party for the speach data was assigned based on their party at the beginning of the congress).