---
title: "Scrape the Congressional Record with `rvest`"
subtitle: 
author: ""
output:
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Scrape URLs for every bit of the Congressional Record

As we do so, we retain some key metadata 
- The record is divided by date
- The record is divided into three sections: Senate, House, Extensions of Remarks (text submitted to the record later)
- the page number ("S3253" is the 3,253rd page of the recored, featuring remarks from the Senate)

URLs look like this:
"https://www.congress.gov/congressional-record/2017/6/6/senate-section/article/S3253-6"

```{r, eval=FALSE}
# a date range to scrape
dates <- seq(as.Date("2007/01/01"), 
             as.Date("2008/01/01"),
             #Sys.Date(), # today
             by = "day")

# a function to make a data frame of of all cr text urls for a date
get_cr_df <- function(date, section){

  url <- str_c("https://www.congress.gov/congressional-record", 
             date %>% str_replace_all("-", "/"), 
             section, sep = "/")

  pages <- read_html(url) %>%
    html_nodes("a")
  
d <- tibble(header = html_text(pages),
            date = date,
            section = section,
            url = str_c("https://www.congress.gov", 
                         html_attr(pages, "href")
                         )
            ) %>% 
  # trim down to html txt pages
  filter(url %>% str_detect("article")) 

return(d)
}

  ## For testing
    # section <- "senate-section"
    # date <- "2020-09-15"
    # get_cr_df(date, section)

# an empty dataframe for failed calls
d_init <-  tibble(header = "",
                  date = as.Date(NA),
                  section = "",
                  url = "")

# a dataframe of headers, dates, and url paths
senate <- map_dfr(dates, .f = possibly(get_cr_df, otherwise = d_init), section = "senate-section") 

house <- map_dfr(dates, .f = possibly(get_cr_df, otherwise = d_init), section = "house-section") 

ext <- map_dfr(dates, .f = possibly(get_cr_df, otherwise = d_init), section = "extensions-of-remarks-section") 

cr_metadata <- full_join(senate, house) %>% 
  full_join(ext)

# drop dates where for which there is no record
cr_metadata %<>% filter(header != "")
```

```{r save, eval=FALSE}
  d <- cr_metadata
  load(here::here("data", "cr_metadata.Rdata"))
  cr_metadata %<>% full_join(d)
  save(cr_metadata, file = here::here("data", "cr_metadata.Rdata"))
```

# Download the text of the congressional record

The "View TXT in new window" url will take you to an .htm file of just the congressional record text. Compared to the much larger .html of the main page, the (very small) downside is that some of the header information is lost (nothing distinguishes main headers from subheaders).

```{r download_htm, eval = FALSE}
# already downloaded 
downloaded <- list.files(here::here("data", "htm"))

# a function to download htm
get_cr_htm <- function(url){
  
  ## test
  # url <- "https://www.congress.gov/congressional-record/2020/03/02/senate-section/article/S1255-1"
  
  # follow the link to the txt htm 
  url %<>% 
    html_session() %>%
    follow_link("View TXT in new window")
  
  # name files the end of the url 
  file <- str_remove(url$url, ".*modified/")
  
  # if the file has not already been downloaded
  if(!file %in% downloaded){
      read_html(url) %>% 
      write_html(file = here::here("data","htm", file))
  }
}

## test 
# get_cr_htm(cr_metadata$url[1])

walk(cr_metadata$url, get_cr_htm)
```

# Download the full HTML

The full HTML of the main page appears to have some metadata beyond the TXT files. 
- main subject headers 
- possibly speaker id's (speeches appear to be tagged with member id's, but I have yet to find them)

However, the full HTML is several GB per year. 

```{r download_html, eval = FALSE}
# make file path
cr_metadata %<>% 
  mutate(file = str_c("CREC-", 
                      date,"-",
                      # the file title
                      url %>% str_remove(".*article/"), 
                      ".html"))

# already downloaded 
downloaded <- list.files(here::here("data", "html"))

# a function to download html
get_cr_html <- function(url, file){
  message(url)
  if(!file %in% downloaded){
    url %>% 
      read_html() %>% 
      write_html(file = here::here("data", "html",file)
  }
}

## test 
# get_cr(d$url[2], d$file[2])

start <- Sys.time()
walk2(cr_metadata$url, cr_metadata$file, get_cr_html)
Sys.time() - start
```

# Number of documents over time


```{r, include=FALSE, eval = TRUE}
# load cached data
load(here::here("data", "cr_metadata.Rdata"))
```

In all, we have `r nrow(cr_metadata)` documents from `r min(cr_metadata$date)` to `r max(cr_metadata$date)`.

### By day

```{r cr_sections-day}
# for plotting
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 

cr_metadata %>% 
  ggplot() + 
  aes(x = date) +
  geom_bar() + 
  facet_wrap("chamber", ncol = 1, scales = "free_y") 
```

### By year

```{r cr_sections_year}
# for plotting
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 

cr_metadata %>% 
  ggplot() + 
  aes(x = year) +
  geom_bar() + 
  facet_wrap("chamber", ncol = 1)
```

## Headers mentioning COVID19
```{r covid}
cr_metadata %<>% 
  # id sections about COVID19
  mutate(covid = ifelse(str_detect(header, "COVID|CORONA"), "COVID19", "Other") )

cr_metadata %>% 
  filter(date > as.Date("2019-10-01"), 
         chamber != "Extensions of Remarks") %>% 
  ggplot() + 
  aes(x = date, fill = covid) +
  geom_bar() +
  labs(fill = "") + 
  facet_grid(covid ~ chamber, scales = "free_y") 
```

`r cr_metadata %>% filter(covid == "COVID19") %>% nrow()` documents have "COVID" or "coronavirus" in their header.

## Most common headers
```{r cr_subtypes}
# clean up headers 
cr_metadata %<>% 
         mutate(subtype = header %>% 
           toupper() %>% 
           str_remove(";.*") %>% 
           str_replace(".*ACT.*", "ACT") %>% 
             str_replace("MESSAGE ", "MESSAGES ") %>%
             str_replace("CONDEMNING.*", "CONDEMNING") %>%
           str_remove_all(" BY .*| UNTIL.*| \\(EXECUTIVE.*")
         )

# top 100 headers
cr_metadata %>% 
  count(subtype, sort = T) %>% 
  head(100) %>% 
  kablebox()

top10 <- cr_metadata %>% count(subtype, sort = T) %>% .$subtype %>% head(10)

cr_metadata %>% 
  filter(subtype %in% top10) %>% 
  ggplot() + 
  aes(x = date, fill = subtype) +
  geom_bar(width = .9) +
  labs(fill = "Most common topics") + 
  facet_wrap("chamber", ncol = 1, scales = "free")
```

## Most discussed acts
```{r cr_acts, fig.width = 10}
# top 100 headers
cr_metadata %>% 
  filter(str_detect(header, " ACT( |$)")) %>%
  count(header, sort = T) %>% 
  head(100) %>% 
  kablebox()

top10 <- cr_metadata %>% 
  filter(str_detect(header, " ACT( |$)")) %>%
  count(header, sort = T) %>% .$header %>% head(10)

cr_metadata %>% 
  filter(header %in% top10) %>% 
  mutate(header = header %>% str_remove(";.*")) %>%
  ggplot() + 
  aes(x = factor(year), fill = header) +
  geom_bar(width = .9) +
  labs(fill = "Most discussed acts",
       x = "Year") + 
  facet_wrap("chamber", ncol = 1, scales = "free_y") 
```
