---
title: "Speakers in the Congressional Recored"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = TRUE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

Data scraped using this script: https://judgelord.github.io/cr/scraper.html

```{r}
# metadata
load(here::here("data", "cr_metadata.Rdata"))

# clean up data for plot clarity
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4) %>% as.numeric(),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 



# load cr text file names
cr <- list.files("/Users/devin/cr_bulk/data/htm")

# extract date from file name
d <- tibble(file = cr,
            year = str_extract(cr, "[0-9]{4}") %>% as.numeric(),
            date = str_extract(cr, "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% 
         as.Date() ) 

d %<>% arrange(date) %>% arrange(rev(date))

#FIXME
# just using 1000 documents for now
d %<>% top_n(500, date)
# /FIXME

# reconstruct URLs
d %<>% mutate(url_txt = str_c("https://www.congress.gov/117/crec/", 
                          date %>% str_replace_all("-", "/"), 
                          "/modified/", 
                          file))


# a function to get the first bit of text
head_text <- function(file){

  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish() %>% 
    str_remove(".*?www.gpo.gov</a>\\] ") %>% 
    str_sub(0, 500) %>% 
    str_c("...")

  return(text)
}

## test
# head_text(d$file[5])



# Extract speaker names

# a function to grab speaker names
extract_names <- function(file){
  
  names <- "(Mr.|Mrs.|Ms.|Miss|HON.) (([A-Z]|\\.| )* |-|)(Mc|Mac|Des|De|La|[A-Z])[A-Z][A-Z]+|The PRESIDING OFFICER|The SPEAKER pro tempore \\(.*?\\)|The ACTING PRESIDENT|The VICE PRESIDENT"
  
  # for testing 
  #file <- d$file[41]
  
  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish()
  text
  
  if( str_detect(text, names) ){
     text %<>%
      str_extract_all(names) %>% 
      unlist() %>% 
      # drop first letter of first sentence
      str_remove("\\. [A-Z]$|\\.$") %>% 
      str_squish() %>% 
      unique() %>% 
      str_c(collapse = ";") %>% 
      str_sub(0, 240)
  } else {
    text <- "NA"
  }
    
  return(text)
}

## Test
# extract_names(d$file[46])

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "")))


d$text <- d$file %>% map_chr(possibly(head_text, otherwise = ""))

# extract names
# cr_metadata %<>%
#   mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "")))

############################################
# join metadata to file names 
#FIXME for some reason, urls without a -[1-9] at the end seem to be missing from the metadata
d %<>% left_join(cr_metadata) 

d %>% 
  filter(!str_detect(speaker,";.*;"), 
         speaker != "NA") %>% 
  select(speaker, text, url_txt) %>% kablebox()
```

---

## Most frequent speakers from `r min(d$date)` to `r max(d$date)`

```{r}
d %>% 
  filter(speaker != "NA") %>% 
  count(speaker, sort = T) %>% head(20) %>% kablebox()
```

---

## Multiple speakers?

```{r}
d %>% 
  filter(str_detect(speaker, ";.*;")) %>% 
  select(url_txt, speaker) %>% kablebox()
```

---

## No speaker? 

```{r}
d %>% 
  filter(speaker == "NA") %>% 
  select(speaker, text, url_txt) %>% kablebox()
```

## To Do

1. Exclude prayer, the pledge, the journal, resignation, adjournment, executive communications, announcements, communications, appointment, reappointment, recess, recall, designations, additional sponsors, and other proceedural sections.

1. Parse sections with more than one speaker, starting with "[SPEAKER NAME]. (Mister|Madam) Speaker, ". For example, see the Impeachment speaches, where speakers yield time to other speakers.

1. Check members with irregular capitalization beyond "Mc|Mac|Des|De|La"

1. Match speaker names to ICPSR IDs like I did [here](https://judgelord.github.io/cr/speeches) for the hein-bound data using the crosswalk crated [here](https://judgelord.github.io/cr/member_data.html).