---
title: "Speakers in the Congressional Recored"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>% 
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

Data scraped using this script: https://judgelord.github.io/cr/scraper.html

# Parse the Congressional Record

### 0. Metadata from html
```{r html-metadata, cache = TRUE}
# Note, we don't need this metadata to parse the files
# metadata
load(here::here("data", "cr_metadata.Rdata"))

# clean up data for plot clarity
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4) %>% as.numeric(),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 
```


### 1. Metadata from file names

```{r file-metadata, cache=TRUE}
# load cr text file names
cr_file <- list.files("/Users/devin/cr_bulk/data/htm")

# extract date from file name
cr <- tibble(file = cr_file,
            year = str_extract(cr_file, "[0-9]{4}") %>% as.numeric(),
            date = str_extract(cr_file, "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% 
              as.Date() ) 

# get congress from year 
cr %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# extract chamber from URL 
cr %<>% mutate(chamber = str_extract(file, "Pg.") %>% 
                str_remove("Pg") %>%
                str_replace("E", "Extensions of Remarks") %>% 
                str_replace("H", "House") %>% 
                str_replace("S", "Senate") )

# reconstruct URLs from file names
cr %<>% mutate(url_txt = str_c("https://www.congress.gov/", congress, "/crec/", 
                              date %>% str_replace_all("-", "/"), 
                          "/modified/", 
                          file))
```



### 2. Read in text

> NOTE: I'm just using a sample of documents for now.

```{r}
#FIXME
# just using a few documents for now
# d %<>% top_n(22, date)

d <- filter(cr, date == as.Date("2018-03-08") )

d <- d[1:30, ]
# /FIXME


# TEXT AND TEXT VARS 

# a function to get the first bit of text
head_text <- function(file){

  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish() %>% 
    str_remove(".*?www.gpo.gov</a>\\] ") %>% 
    str_sub(0, 500) %>% 
    str_c("...")

  return(text)
}

# a function to get all text
all_text <- function(file){

  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish() %>% 
    str_remove(".*?www.gpo.gov</a>\\] ") 

  return(text)
}

## test
# head_text(d$file[5])

# the first bit of text
d$text_head <- d$file %>% map_chr(possibly(head_text, otherwise = "")) 

# fill in procedural roles
d %<>% 
  mutate(process = str_extract(text_head, "^(ANNOUNCEMENT|RECESS|PRAYER|PLEDGE|MESSAGE|EXECUTIVE MESSAGE|EXECUTIVE COMMUNICATION|EXECUTIVE AND OTHER COMMUNICATION|MEASURE|ADJOURNMENT|DESIGNATION|THE JOURNAL|RESIGNATION|ELECTING|CONSTITUTIONAL|ADDITIONAL SPONSORS|SWEARING IN|MOMENT OF SILENCE|SENATE COMMITTEE MEETING|BUDGETARY|EFFECTS|REAPPOINTMENT|APPOINTMENT|RECALL|COMMUNICATION|REMOTE COMMITTEE PROCEEDINGS|REMOTE VOTING||ENROLLED BILL|ADDITIONAL COSPONSORS|DISCHARGED NOMINATION|CONFIRMATION|JOINT RESOLUTION|SENATE ENROLLED BILLS|PUBLICATION|EXPLANATORY STATEMENT|WITHDRAWAL)") )  



# order by date (just for presentation)
d %<>% arrange(date) %>% arrange(rev(date))
```



### 3. Extract speaker names from text

```{r extract}
# Extract speaker names

# a function to grab speaker names
extract_names <- function(file){
  
  names <- "(Mr.|Mrs.|Ms.|Miss|HON.) (([A-Z]|\\.| )* |-|)(Mc|Mac|Des|De|La|[A-Z])[A-Z][A-Z]+|The PRESIDING OFFICER|The SPEAKER\\.|The SPEAKER pro tempore \\(.*?\\)|The ACTING PRESIDENT|The VICE PRESIDENT"
  
  # for testing 
  #file <- d$file[41]
  
  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish()
  text
  
  #if( str_detect(text, names) ){
     text %<>%
      str_extract_all(names) %>% 
      unlist() %>% 
      # drop first letter of first sentence
      str_remove("\\. [A-Z]$|\\.$") %>% 
      str_squish() %>% 
      #unique() %>% 
      #str_sub(0, 240) %>% # trim just in case pattern overmatches
      str_c(collapse = ";") 
  #} else {
  #  text <- NA
  #}
    
  return(text)
}

## Test
# extract_names(d$file[22])

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "404error")),
         speaker = coalesce(speaker, process))
```

---

#### Multiple speakers?

```{r, cache=FALSE}
d %>% 
  filter(str_detect(speaker, ";")) %>% 
  select(speaker, url_txt) %>% kablebox()
```

---

#### No speaker? 

```{r, cache=FALSE}
d %>% 
  filter(is.na(speaker)|speaker == "") %>% 
  select(speaker, text_head, url_txt) %>% kablebox()
```


### 4. Parse texts with multiple speakers

```{r}
# a function to parse files with more than one speaker
# for testing
# speakers <- d$speaker[22] 
# file <- d$file[22]
parse <- function(speakers, file){
  speakers %<>% str_split(";") %>% unlist()
  
  text <- all_text(file) # all text
  
  speech <- NA # init
  
  for(i in 1:length(speakers)){
    
    # add one to speakers vector to mark the end of the last speach
    s <- c(speakers, "$")

    # speech of speaker i
    speech[i] <- text %>% 
      str_extract(str_c(s[i],".*?", s[i+1])) %>% str_remove(s[i+1]) 
    
    # remove speech i from text
    text %<>% 
      str_remove(str_c(".*?", s[i], "$")) 
  }
  return( list(speech) )
}

## test
# parse(d$speaker[1], d$file[1])

parse_text <- function(d){
d$text <- map2(.x = d$speaker,
               .y = d$file, 
               .f = parse) %>% flatten()

# split speakers into a list 
d$speaker %<>% str_split(";")

# unnest
d %<>% unnest(c(speaker, text)) 

d %<>% distinct()






# extract names
# cr_metadata %<>%
#   mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "")))

############################################
# join metadata to file names 
#FIXME for some reason, urls without a -[1-9] at the end seem to be missing from the metadata

## Commented out because we don't need html metadata to parse
# d %<>% left_join(cr_metadata) 

d %<>% mutate(text_head = text %>% 
                str_sub(0,500) %>% 
                str_c("...") )

return(d)
} #END parse

d %<>% parse_text()

d %>% 
  filter(!str_detect(speaker,";.*;"), 
         !is.na(speaker) ) %>% 
  select(speaker, text_head, url_txt) %>% kablebox()
```

---

### Most frequent speakers from `r min(d$date)` to `r max(d$date)`

```{r, cache=FALSE}
d %>% 
  count(speaker, sort = T) %>% kablebox()
```



# Match with voteview 

```{r}
# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))

# Devin's name matching function 
source(here("code", "nameMethods.R"))

# common typos and known permutations and nicknames 
source(here("code", "MemberNameTypos.R"))

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# clean up speaker names and add chamber titles for better matching
d %<>% mutate(chamber = ifelse(
  chamber == "Extensions of Remarks" &
    str_detect(text_head, "(Mr|Mrs|Ms|Miss)\\. Speaker\\,|in the house of representatives"), "House", "Senate"),
              speaker = speaker %>% 
    str_remove("(^|;)(Mr|Mrs|Ms|Miss|HON)(\\.| )") %>% 
    str_squish())

d %<>% mutate(speaker =
               ifelse(row_number() > 1 & str_detect(lag(speaker),
                                 speaker), 
                      lag(speaker),
                      speaker)) 


d1 <- d %>% extractMemberName(col_name = "speaker", members = members)

d1 %>% 
  select(speaker, bioname, icpsr, chamber) %>%
  distinct() %>% kablebox()
```


# Save text parsed by member name


```{r, eval=FALSE}
cr_write <- function(cr_date){
d <- filter(cr, date == as.Date(cr_date) )

d <- d[1:30, ]

# the first bit of text (faster because proceedural titles area at the beginning, no need to search full text)
d$text_head <- d$file %>% map_chr(possibly(head_text, otherwise = "")) 

# fill in proceedural roles
d %<>% 
  mutate(process = str_extract(text_head, "^(ANNOUNCEMENT|RECESS|PRAYER|PLEDGE|MESSAGE|EXECUTIVE MESSAGE|EXECUTIVE COMMUNICATION|EXECUTIVE AND OTHER COMMUNICATION|MEASURE|ADJOURNMENT|DESIGNATION|THE JOURNAL|RESIGNATION|ELECTING|CONSTITUTIONAL|ADDITIONAL SPONSORS|SWEARING IN|MOMENT OF SILENCE|SENATE COMMITTEE MEETING|BUDGETARY|EFFECTS|REAPPOINTMENT|APPOINTMENT|RECALL|COMMUNICATION|REMOTE COMMITTEE PROCEEDINGS|REMOTE VOTING||ENROLLED BILL|ADDITIONAL COSPONSORS|DISCHARGED NOMINATION|CONFIRMATION|JOINT RESOLUTION|SENATE ENROLLED BILLS|PUBLICATION|EXPLANATORY STATEMENT|WITHDRAWAL)") )  

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "404error")),
         speaker = coalesce(speaker, process))

d %<>% parse_text()

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "404error")),
         speaker = coalesce(speaker, process))

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# clean up speaker names and add chamber titles for better matching
d %<>% mutate(chamber = ifelse(
  chamber == "Extensions of Remarks" &
    str_detect(text_head, "(Mr|Mrs|Ms|Miss)\\. Speaker\\,|in the house of representatives"), "House", "Senate"),
  speaker = speaker %>% 
    str_remove("(^|;)(Mr|Mrs|Ms|Miss|HON)(\\.| )") %>% 
    str_squish() )

d %<>% mutate(speaker =
               ifelse(row_number() > 1 & str_detect(lag(speaker),
                                 speaker), 
                      lag(speaker),
                      speaker)) 


d1 <- d %>% extractMemberName(col_name = "speaker", members = members)

# fill in empty
d1 %<>% 
  mutate(file = file %>% replace_na("CREC-missing"),
         icpsr = icpsr %>% replace_na("NA"))

d1 %<>% mutate(path = str_c("data", 
               "txt", 
               year, 
               icpsr, 
               str_c(file %>% str_remove(".htm"), 
                     "-", ID, "-", icpsr, ".txt"),
               sep = "/"  ))

# make missing directories
make_dir <- function(x){
if(!dir.exists(x)){dir.create(x)}
}

walk(str_remove(d1$path, "/CREC.*"),
     .f = make_dir)

## May want to change directory 
# here(other_dir) %>% str_remove("project_root/")

# save
walk2(d1$text,
      here::here(d1$path),
      .f = write_lines)
}

## One day of the CR
# cr_write("2020-02-06")

## Many days of the CR (e.g. feburary 2020)
dates <- cr %>% filter(str_detect(date, "2020-02")) %>% distinct(date)

walk(dates,
    cr_write)

list.files(here::here("data", "txt"), recursive = T) 
```

## Directory structure for parsed txt
```{r}
# fill in empty
d1 %<>% 
  mutate(file = file %>% replace_na("CREC-missing"),
         icpsr = icpsr %>% as.integer() %>% replace_na(00000))

d1 %<>% mutate(path = str_c("data", 
               "txt", 
               year, 
               icpsr, 
               str_c(file %>% str_remove(".htm"), 
                     "-", ID, "-", icpsr, ".txt"),
               sep = "/"  ))

d1 %>% 
  left_join(members)%>%
  select(bioname, cqlabel, path) %>% kablebox()
```

## To Do

- [x] Exclude prayer, the pledge, the journal, resignation, adjournment, executive communications, announcements, communications, appointment, reappointment, recess, recall, designations, additional sponsors, and other proceedural sections. (These texts are parsed and saved in the "NA" folder.)

- [x] Parse sections with more than one speaker, starting with "[SPEAKER NAME]. (Mister|Madam) Speaker, ". For example, see the Impeachment speaches, where speakers yield time to other speakers.

- [ ] Check members with irregular capitalization beyond "Mc|Mac|Des|De|La"

- [x] Match speaker names to ICPSR IDs like I did [here](https://judgelord.github.io/cr/speeches) for the hein-bound data using the crosswalk crated [here](https://judgelord.github.io/cr/member_data.html).

- [ ] Names to fix in function: Susan *W.* Brrooks

