---
title: "Speakers in the Congressional Recored"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>% 
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

Data scraped using this script: https://judgelord.github.io/cr/scraper.html

# Parse the Congressional Record

### 0. Metadata from html
```{r html-metadata, cache = TRUE}
# Note, we don't need this metadata to parse the files
# metadata
load(here::here("data", "cr_metadata.Rdata"))

# clean up data for plot clarity
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4) %>% as.numeric(),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 
```


### 1. Metadata from file names

```{r file-metadata, cache=TRUE}
# load cr text file names
cr <- list.files("/Users/devin/cr_bulk/data/htm")

# extract date from file name
d <- tibble(file = cr,
            year = str_extract(cr, "[0-9]{4}") %>% as.numeric(),
            date = str_extract(cr, "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% 
         as.Date() ) 

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# extract chamber from URL 
d %<>% mutate(chamber = str_extract(file, "Pg.") %>% 
                str_remove("Pg") %>%
                str_replace("E", "Extensions of Remarks") %>% 
                str_replace("H", "House") %>% 
                str_replace("S", "Senate") )

# reconstruct URLs from file names
d %<>% mutate(url_txt = str_c("https://www.congress.gov/", congress, "/crec/", 
                              date %>% str_replace_all("-", "/"), 
                          "/modified/", 
                          file))
```



### 2. Read in text

> I'm just using a sample of documents for now.

```{r}
#FIXME
# just using a few documents for now
# d %<>% top_n(22, date)

d %<>% filter(date == as.Date("2018-03-08") )

d <- d[1:30, ]
# /FIXME


# TEXT AND TEXT VARS 

# a function to get the first bit of text
head_text <- function(file){

  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish() %>% 
    str_remove(".*?www.gpo.gov</a>\\] ") %>% 
    str_sub(0, 500) %>% 
    str_c("...")

  return(text)
}

# a function to get all text
all_text <- function(file){

  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish() %>% 
    str_remove(".*?www.gpo.gov</a>\\] ") 

  return(text)
}

## test
# head_text(d$file[5])

# the first bit of text
d$text_head <- d$file %>% map_chr(possibly(head_text, otherwise = "")) 

# fill in proceedural roles
d %<>% 
  mutate(process = str_extract(text_head, "^(ANNOUNCEMENT|RECESS|PRAYER|PLEDGE|MESSAGE|EXECUTIVE MESSAGE|EXECUTIVE COMMUNICATION|EXECUTIVE AND OTHER COMMUNICATION|MEASURE|ADJOURNMENT|DESIGNATION|THE JOURNAL|RESIGNATION|ELECTING|CONSTITUTIONAL|ADDITIONAL SPONSORS|SWEARING IN|MOMENT OF SILENCE|SENATE COMMITTEE MEETING|BUDGETARY|EFFECTS|REAPPOINTMENT|APPOINTMENT|RECALL|COMMUNICATION|REMOTE COMMITTEE PROCEEDINGS|REMOTE VOTING||ENROLLED BILL|ADDITIONAL COSPONSORS|DISCHARGED NOMINATION|CONFIRMATION|JOINT RESOLUTION|SENATE ENROLLED BILLS|PUBLICATION|EXPLANATORY STATEMENT|WITHDRAWAL)") )  



# order by date (just for presentation)
d %<>% arrange(date) %>% arrange(rev(date))
```



### 3. Extract speaker names from text

```{r extract}
# Extract speaker names

# a function to grab speaker names
extract_names <- function(file){
  
  names <- "(Mr.|Mrs.|Ms.|Miss|HON.) (([A-Z]|\\.| )* |-|)(Mc|Mac|Des|De|La|[A-Z])[A-Z][A-Z]+|The PRESIDING OFFICER|The SPEAKER\\.|The SPEAKER pro tempore \\(.*?\\)|The ACTING PRESIDENT|The VICE PRESIDENT"
  
  # for testing 
  #file <- d$file[41]
  
  text <- read_lines(str_c("/Users/devin/cr_bulk/data/htm/", file)) %>% 
    str_c(collapse = " ") %>% 
    str_squish()
  text
  
  #if( str_detect(text, names) ){
     text %<>%
      str_extract_all(names) %>% 
      unlist() %>% 
      # drop first letter of first sentence
      str_remove("\\. [A-Z]$|\\.$") %>% 
      str_squish() %>% 
      #unique() %>% 
      #str_sub(0, 240) %>% # trim just in case pattern overmatches
      str_c(collapse = ";") 
  #} else {
  #  text <- NA
  #}
    
  return(text)
}

## Test
# extract_names(d$file[22])

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "404error")),
         speaker = coalesce(speaker, process))
```

---

#### Multiple speakers?

```{r, cache=FALSE}
d %>% 
  filter(str_detect(speaker, ";")) %>% 
  select(speaker, url_txt) %>% kablebox()
```

---

#### No speaker? 

```{r, cache=FALSE}
d %>% 
  filter(is.na(speaker)|speaker == "") %>% 
  select(speaker, text_head, url_txt) %>% kablebox()
```


### 4. Parse texts with multiple speakers

```{r}
# a function to parse files with more than one speaker
# for testing
# speakers <- d$speaker[22] 
# file <- d$file[22]
parse <- function(speakers, file){
  speakers %<>% str_split(";") %>% unlist()
  
  text <- all_text(file) # all text
  
  speech <- NA # init
  
  for(i in 1:length(speakers)){
    
    # add one to speakers vector to mark the end of the last speach
    s <- c(speakers, "$")

    # speech of speaker i
    speech[i] <- text %>% 
      str_extract(str_c(s[i],".*?", s[i+1])) %>% str_remove(s[i+1]) 
    
    # remove speech i from text
    text %<>% 
      str_remove(str_c(".*?", s[i], "$")) 
  }
  return( list(speech) )
}

## test
# parse(d$speaker[1], d$file[1])

d$text <- map2(.x = d$speaker,
               .y = d$file, 
               .f = parse) %>% flatten()

# split speakers into a list 
d$speaker %<>% str_split(";")

# unnest
d %<>% unnest(c(speaker, text)) 

d %<>% distinct()






# extract names
# cr_metadata %<>%
#   mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "")))

############################################
# join metadata to file names 
#FIXME for some reason, urls without a -[1-9] at the end seem to be missing from the metadata

## Commented out because we don't need html metadata to parse
# d %<>% left_join(cr_metadata) 

d %<>% mutate(text_head = text %>% 
                str_sub(0,500) %>% 
                str_c("...") )

d %>% 
  filter(!str_detect(speaker,";.*;"), 
         !is.na(speaker) ) %>% 
  select(speaker, text_head, url_txt) %>% kablebox()
```

---

### Most frequent speakers from `r min(d$date)` to `r max(d$date)`

```{r, cache=FALSE}
d %>% 
  count(speaker, sort = T) %>% kablebox()
```



# Match with voteview 

```{r}
# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))

# Devin's name matching function 
source(here("code", "nameMethods.R"))

# common typos and known permutations and nicknames 
source(here("code", "MemberNameTypos.R"))

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# clean up speaker names and add chamber titles for better matching
d %<>% mutate(chamber = ifelse(
  chamber == "Extensions of Remarks" &
    str_detect(text_head, "(Mr|Mrs|Ms|Miss)\\. Speaker\\,|in the house of representatives"), "House", "Senate"),
              speaker = speaker %>% 
    str_remove("(^|;)(Mr|Mrs|Ms|Miss|HON)(\\.| )") %>% 
    str_squish())

d %<>% mutate(speaker =
               ifelse(row_number() > 1 & str_detect(lag(speaker),
                                 speaker), 
                      lag(speaker),
                      speaker)) 


d1 <- d %>% extractMemberName(col_name = "speaker", members = members)

d1 %>% 
  select(speaker, bioname, icpsr, chamber) %>%
  distinct() %>% kablebox()
```

## To Do

- [x] Exclude prayer, the pledge, the journal, resignation, adjournment, executive communications, announcements, communications, appointment, reappointment, recess, recall, designations, additional sponsors, and other proceedural sections.

- [x] Parse sections with more than one speaker, starting with "[SPEAKER NAME]. (Mister|Madam) Speaker, ". For example, see the Impeachment speaches, where speakers yield time to other speakers.

- [ ] Check members with irregular capitalization beyond "Mc|Mac|Des|De|La"

- [x] Match speaker names to ICPSR IDs like I did [here](https://judgelord.github.io/cr/speeches) for the hein-bound data using the crosswalk crated [here](https://judgelord.github.io/cr/member_data.html).