---
title: "Legislator behavior by district characteristics"
subtitle: 
author: ""
output:
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    html_document:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>%  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

I'm just using Hein-bound speech data for now; I'll replace this with our data scraped from the Congressional Record when we nail down exactly what we want to extract from speeches.

```{r}
# a function to read speeches and speaker data 
get_speeches <- function(file){
  
  message(file)
  
  read_delim(str_c(here("hein-bound/", file) %>% str_remove("/cr") ),
             delim = "|") %>% 
  # extract congress from file name
  mutate(congress = str_remove(file, "_.*") ) %>% 
    select(speakerid, speech_id, congress) %>% 
  distinct()
}

# files 
heinbound <- list.files(here("hein-bound") %>% str_remove("/cr") ) %>% 
  enframe(value = "file")

# subset to speakermap files from recent congresses
speakermaps <- heinbound %>% 
  filter(str_detect(file, "SpeakerMap"),
         str_detect(file, "^1") #FIXME subsetting to >99th congress
         )

# speakers dataframe
speeches <- map_dfr(speakermaps$file, get_speeches)

speeches$congress %<>% as.numeric()

# FIXME focusing on the 107-111th for now 
speeches %<>% 
  filter(congress > 106)


# Devin's members data (expanded from voteview)
load(here("data", "members.Rdata"))

# Make mixed case names, like "McConnell" upper case (to go the other way, we would need to fix them one by one)
members %<>% 
  mutate(last_name = str_to_upper(last_name),
         party = str_sub(party_name, 1, 1))

# GET CROSSWALK
load(here::here("data", "crosswalk.Rdata") )

speeches %<>% 
  select(congress, speakerid, speech_id) %>% 
  distinct() %>% 
  count(congress, speakerid) %>% 
  # Add ICPSRs 
  left_join(crosswalk) %>% 
  # add NOMINATE
  left_join(members %>% 
              select(chamber, party, icpsr, nominate.dim1) %>% 
              distinct() ) %>% 
  mutate(name = bioname %>% str_remove(",.*") %>% str_to_title() ) %>% 
  filter(party %in% c("D", "R"))
```

## Number of Speeches by NOMINATE Score 2001-2011
```{r speeches_nominate}
plot_speeches <- function(data, var, lab){
  
data %>%
    mutate(x = pull(data, var)) %>% 
  ggplot() + 
  aes(x = x, y = n, label = name, color = party) + 
  geom_point(alpha = .2) + 
      geom_smooth() + 
  geom_text(check_overlap = T, color = "black") + 
  labs(y = "Number of Speeches per Congress",
       x = lab,
       color = "Party") +
  scale_color_manual(values=c("#0015BC", "#FF0000")) 
}

plot_speeches_congress <- function(data, var, lab){

data %>% 
  mutate(x = pull(data, var)) %>% 
  ggplot() + 
  aes(x = x, y = n, label = name, color = party) + 
  geom_point(alpha = .2) + 
  geom_text(check_overlap = T, color = "black") + 
  labs(y = "Number of Speeches per Congress",
       x = lab,
       color = "Party") +
  scale_color_manual(values=c("#0015BC", "#FF0000")) + 
    facet_wrap("congress", scales = "free")
}

plot_speeches(data = speeches, var = "nominate.dim1", lab = "NOMINATE 1 Score")

plot_speeches_congress(speeches, "nominate.dim1", "NOMINATE 1 Score")
```

## Vote share data from [MIT Elections Lab](https://electionlab.mit.edu/data)

```{r}
house <- read_csv(here::here("data", "voteshare", "1976-2018-house3.csv"))

house %<>% filter(stage == "gen", 
                  party %in% c("DEMOCRAT", "REPUBLICAN"),
                  !runoff,
                  !special)

house %<>%  mutate(congress = as.numeric(round((year - 2000.1)/2)) + 107) # the 107th congress began in 2001 and we want the congress after the election 

house %<>%  mutate(congress_year = as.numeric(round( (congress - 107)*2 + 2001 ))) # the 107th congress began in 2001 and we want the congress after the election 


# align with voteview
house %<>% 
  mutate(party = str_sub(party, 1, 1)) %>% 
  rename(state_abbrev = state_po) %>% 
  mutate(district_code = district) 

house2 <- house %>% 
  group_by(congress, party, state_abbrev, district_code) %>% 
  summarise(votes = sum(candidatevotes) ) %>% 
  ungroup() %>% 
  group_by(congress, state_abbrev, district_code) %>% 
  mutate(twoparty = sum(votes),
         share = votes/twoparty) %>% 
  ungroup()

speeches %<>% 
  filter(chamber == "House") %>% 
  left_join(house2)  # %>% select(bioname, state_abbrev, district_code, chamber, share) %>% filter(is.na(share))


## inspect candidates who won with < 40% pres vote for their party 
#speeches %>% filter(share < .4) %>% select(bioname,  congress)
```

### Number of Speeches by Vote Share
```{r speeches_voteshare}
speeches %>% plot_speeches("share", "Two-party Vote Share")
```

### Number of Speeches by Vote Share in Contested Races
```{r speeches_voteshare_contested}
speeches %>% 
  filter(share < 1) %>% 
  plot_speeches("share", "Two-party Vote Share in Contested Races")
```

### Number of Speeches by Co-partisan Presidential Vote Share

```{r speeches_voteshare_pres}

pres <- read_csv(here::here("data", "voteshare", "1976-2016-president.csv"))

pres %<>% 
  # just dem and gop (not other parties "e.g. democrat-farmer-labor"
  mutate(party = str_remove(party, "-.*|ic-.*")) %>% 
  filter(party %in% c("democrat", "republican") )

pres %<>%  mutate(congress = as.numeric(round((year - 2000.1)/2)) + 107) # the 107th congress began in 2001 and we want the congress after the election 


# align with voteview
pres %<>% 
  mutate(party = str_sub(party, 1, 1) %>% toupper() ) %>% 
  rename(state_abbrev = state_po) 

pres2 <- pres %>% 
  group_by(congress, party, state_abbrev) %>% 
  summarise(votes_pres = sum(candidatevotes) ) %>% 
  ungroup() %>% 
  group_by(congress, state_abbrev) %>% 
  mutate(twoparty_pres = sum(votes_pres),
         share_pres = votes_pres/twoparty_pres) %>% 
  ungroup()

speeches %<>% 
  left_join(pres2)  # %>% select(bioname, state_abbrev, district_code, chamber, share) %>% filter(is.na(share))

# # candidates who won with < 40% pres vote for their party 
# speeches %>% filter(share_pres < .4) %>% select(bioname,  congress)

speeches %>% plot_speeches("share_pres", "Co-partisan Share of Two-party Presidential Vote Share")
```